Fluent statistical computing interfaces for biological data analysis

### 2020-07-19 Rmd/05-embeddings.Rmd
add video, reduce PDF size with mp4

```{r setup-videos, cache = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", here::here("video", "liminal-gaussian.mov"),
  "hierachical", "https://player.vimeo.com/video/439635905", here::here("video", "liminal-hierachical.mov"),
  "trees-01", "https://player.vimeo.com/video/439635892", here::here("video", "liminal-trees-01.mov"),
  "trees-02", "https://player.vimeo.com/video/439635863", here::here("video", "liminal-trees-02.mov"),
  "mouse-01", "https://player.vimeo.com/video/439635812", here::here("video", "liminal-mouse-01.mov"),
  "mouse-02", "https://player.vimeo.com/video/439635843", here::here("video", "liminal-mouse-02.mov")
)

@@

display_vid_latex <- function(key, lookup) {
    video <- lookup[lookup$key == key, ]
    glue::glue(
    "\\begin{{center}}
   \\includemedia[
    width=0.6\\linewidth,
    height=0.4\\linewidth,
    keepaspectratio=true,
    addresource={video},
    flashvars={{%
      source={video}
      &autohide=1
      &autoPlay=true
      &loop=true}
  ]{{}}{{VPlayer.swf}}
  \\end{{center}}",
  video = video[["path"]]
  )
}

>>>>

```{r setup-videos, cache = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", here::here("video", "liminal-gaussian.mp4"),
  "hierachical", "https://player.vimeo.com/video/439635905", here::here("video", "liminal-hierachical.mp4"),
  "trees-01", "https://player.vimeo.com/video/439635892", here::here("video", "liminal-trees-01.mp4"),
  "trees-02", "https://player.vimeo.com/video/439635863", here::here("video", "liminal-trees-02.mp4"),
  "mouse-01", "https://player.vimeo.com/video/439635812", here::here("video", "liminal-mouse-01.mp4"),
  "mouse-02", "https://player.vimeo.com/video/439635843", here::here("video", "liminal-mouse-02.mp4")
)

@@

display_vid_latex <- function(key, lookup) {
    video <- lookup[lookup$key == key, ]
    glue::glue(
    "\\begin{{center}}
   \\includemedia[
    width=0.6\\linewidth,
    height=0.45\\linewidth,
    keepaspectratio=true,
    activate=pageopen
    addresource={video},
    flashvars={{%
      source={video}
      &autoPlay=true
      &loop=true}
  ]{{}}{{VPlayer.swf}}
  \\end{{center}}",
  video = video[["path"]]
  )
}
